---
title: "Lab06 Write-Up"
author: "Sherry Huang"
output: 
  pdf_document: 
    highlight: pygments
    dev: cairo_pdf
fontsize: 11pt
geometry: margin=1in
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidymodels)
```

# Part 1: Nonlinear Regression

```{r theme}
lab06_theme = theme_minimal() + 
  theme(text = element_text(family = "serif", size = 12))
```

```{r}
data = read_csv("swarthmore.csv", col_names = FALSE)
```


```{r}
ggplot(data, aes(x = X1, y = X2)) + 
  geom_point() +
  geom_smooth(method = "gam", se = FALSE, aes(col = "GAM")) +
  geom_smooth(method = "loess", span = .2, se = FALSE, aes(col = "Loess")) +
  geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = FALSE, aes(col = "Quadratic")) +
  geom_smooth(method = "lm", se = FALSE, alpha =.2, aes(col = "OLS")) +
  lab06_theme + 
  scale_color_viridis_d("Model", end = .75, option = "C")
```

# Part 2: Density Plots

```{r}
set.seed(011221)
samples = data.frame(matrix(rnorm(1000), ncol = 10))
colnames(samples) = paste0("sample", 1:10)
samples = tibble(samples)
samples %>%
  pivot_longer(1:10) %>%
  ggplot(., aes(x = value, fill = name)) + 
  geom_histogram() + 
  facet_wrap(vars(name)) + 
  scale_fill_viridis_d(end = .75, option = "C") + 
  lab06_theme + 
  theme(legend.position = "none")
```

```{r}
samples %>%
  pivot_longer(1:10) %>%
  ggplot(., aes(x = value, fill = name)) + 
  geom_histogram(aes(y = ..density..)) + 
  geom_density(alpha = .3, bw = .4, aes(col = name)) +
  facet_wrap(vars(name)) + 
  scale_fill_viridis_d(end = .75, option = "C") + 
  scale_color_viridis_d(end = .75, option = "C") + 
  lab06_theme + 
  theme(legend.position = "none")
```

```{r}
samples %>%
  pivot_longer(1:10) %>%
  ggplot(., aes(y = value, x = name, fill = name)) + 
  geom_boxplot(alpha = .7) + 
  scale_fill_viridis_d(end = .75, option = "C") + 
  scale_color_viridis_d(end = .75, option = "C") + 
  lab06_theme + 
  theme(legend.position = "none")
```

```{r}
samples %>%
  pivot_longer(1:10) %>%
  ggplot(., aes(y = value, x = name, fill = name)) + 
  geom_boxplot(alpha = .7) + 
  geom_jitter(alpha = 0.5, aes(col = name)) +
  scale_fill_viridis_d(end = .75, option = "C") + 
  scale_color_viridis_d(end = .75, option = "C") + 
  lab06_theme + 
  theme(legend.position = "none")
```

```{r}
samples %>%
  pivot_longer(1:10) %>%
  ggplot(., aes(y = value, x = name, fill = name)) + 
  geom_violin(alpha = .6) + 
  geom_jitter(alpha = 0.5, aes(col = name)) +
  scale_fill_viridis_d(end = .75, option = "C") + 
  scale_color_viridis_d(end = .75, option = "C") + 
  lab06_theme + 
  theme(legend.position = "none")
```

```{r}
library(ggridges)
samples %>%
  pivot_longer(1:10) %>%
  ggplot(., aes(y = name, x = value, fill = name)) + 
  geom_density_ridges(alpha = .8) +
  scale_fill_viridis_d(end = .75, option = "C") + 
  scale_color_viridis_d(end = .75, option = "C") + 
  lab06_theme + 
  theme(legend.position = "none")
```

# Part 3: Open-ended

Reminder: here you'll use the `gapminder` data: 

```{r}
library(gapminder)
head(gapminder)
```

## Nonlinear smoothers

Find two variables from the `gapminder`, make a scatterplot, add a `geom_smooth` layer with a linear relationship and a `geom_smooth` layer with a nonlinear relationship (your choice!). Which fits better? Add colors and a legend. 

```{r}
ggplot(data = gapminder, mapping = aes(x = pop, y = lifeExp)) + 
  geom_point() +
  #geom_smooth(method = "gam", se = FALSE, aes(col = "GAM")) +
  geom_smooth(method = "loess", span = .2, se = FALSE, aes(col = "Loess")) +
  #geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = FALSE, aes(col = "Quadratic")) +
  geom_smooth(method = "lm", se = FALSE, alpha =.2, aes(col = "OLS")) +
  lab06_theme + 
  scale_color_viridis_d("Model", end = .75, option = "C") +
  labs(title = "Relationship Between Population and Life Expectancy",
       subtitle = "fitted with linear and non-linear models",
       x = "population",
       y = "life expectancy")
```
 
I think the Loess model fits the data better because it follows the trend of the data better than the OLS model. While the OLS model shows a very general positive, linear correlation between population and expectancy, the Loess model shows the ups and downs and non-linear correlation between population and life expectancy.
 
## Density 

Choose a variable (or combination of variables) from the `gapminder` dataset and make either a kernel density plot, violin plot, or density ridges plot. Write 1-2 sentences summarizing your findings. 

```{r}
ggplot(gapminder, aes(y = continent, x = gdpPercap, fill = continent)) + 
  geom_density_ridges(alpha = .8) +
  scale_fill_viridis_d(end = .75, option = "C") + 
  scale_color_viridis_d(end = .75, option = "C") + 
  lab06_theme +
  theme(legend.position = "none") +
  labs(title = "Probability of GDPs in Each Continent",
       x = "GDP Per Capita",
       y = "continent")
```

This density ridges plot shows the probability of a specific continent having a certain GDP per capita; for example, we can see that for Oceania, $18000$ is the GDP with the highest probability. Something else to note would be the "bumps" in the plot; you can see in Asia, there's a very tall bump close to $0$, showing that there's a LOT of poor countries, but there's a second bump near the $20000$ mark, showing that there's also a significant number of wealthier countries in Asia.