---
title: "Lab04 Write-Up"
author: "Sherry Huang"
output: 
  pdf_document: 
    highlight: pygments
fontsize: 11pt
geometry: margin=1in
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(extrafont)
```


# Part 1: Changing the font

```{r font}
library(palmerpenguins)
ggplot(penguins, aes(y=island, fill = island)) + 
  geom_bar() + 
  theme(text = element_text(family = "Georgia"))
```

I changed the font to Georgia.

# Part 2: `annotate`

```{r annotate}
ggplot(penguins, aes(y=island, fill = island)) + 
  geom_bar() + 
  theme(text = element_text(family = "serif")) +
  annotate("text", # What type of annotation to use 
           x = c(15, 15, 15), # X positions of annotations
           y =c("Torgersen", "Dream", "Biscoe"), # Y positions of annotations (weird because this is a barchart)
           label =c("Torgersen", "Dream", "Biscoe")) + # Labels for annotations 
  theme(legend.position = "none") # Gets rid of the legend 
```

# Part 3

## First customized plot

```{r open-ended-1}
# YOUR CODE HERE
library(socviz)
library(ggthemes)
county_level_2020 = read_csv("https://raw.githubusercontent.com/tonmcg/US_County_Level_Election_Results_08-20/master/2020_US_County_Level_Presidential_Results.csv")

theme_map <- function(base_size=9, base_family="") {
    require(grid)
    theme_bw(base_size=base_size, base_family=base_family) %+replace%
        theme(axis.line=element_blank(),
              axis.text=element_blank(),
              axis.ticks=element_blank(),
              axis.title=element_blank(),
              panel.background=element_blank(),
              panel.border=element_blank(),
              panel.grid=element_blank(),
              panel.spacing=unit(0, "lines"),
              plot.background=element_blank(),
              legend.justification = c(0,0),
              legend.position = c(0,0)
              )
}

county_map_and_data = left_join(county_map, county_level_2020, by = c("id" = "county_fips"))

county_map_and_data <- county_map_and_data %>%mutate(d_points = (per_dem - per_gop)*100)

election2020_p <- ggplot(data = county_map_and_data,
            mapping = aes(x = long, y = lat, fill = d_points, 
                          group = group))
election2020_p1 <- election2020_p + geom_polygon(color = "gray90", size = 0.05) + coord_equal()
election2020_p2 <- election2020_p1 + scale_fill_gradient2() + labs(title = "2020 Election Winning Margins by County")

election2020_p2 + labs(fill = "Percent Difference") +
    theme_map() + theme_tufte() + theme(legend.position = "bottom", text = element_text(family = "Georgia"))
```

I took this map from my Lab 3, and I changed the theme to Tufte, and I also changed the font to Georgia. I didn't change the colors here because the colors represent each respective color's party, and doing so would probably confuse the audience.

## Second customized plot

```{r open-ended-2}
# YOUR CODE HERE
library(viridis)
ggplot(data = diamonds) +
  geom_bar(mapping = aes(x = cut, fill = cut), width = 1) +
  coord_polar() +
  scale_fill_brewer(palette = "Set3") +
  theme_excel() +
  theme(legend.position = "bottom", text = element_text(family = "Tahoma")) +
  labs(title = "Frequencies of Diamond Cuts",
       subtitle = "shown with polar Coordinates")
```

I took this graph from one of the primers, and I changed the theme, font, and color. I don't particularly like the gray background because it's hard to read the labels on the graph, but I think those labels are redundant here anyways, as the legend also displays that information.

## Third customized plot

```{r open-ended-3}
# YOUR CODE HERE
ggplot(data = diamonds) +
  geom_bar(mapping = aes(x = cut, fill = clarity), position = "dodge") +
  theme_fivethirtyeight() +
  theme(text = element_text(family = "AppleMyungjo")) +
  scale_fill_brewer(palette = "PuOr")
```

I took this graph from one of the primers, and I changed the theme to FiveThirtyEight, I changed the color palette, and I also changed the font.