---
title: "Lab08 Write-Up"
author: "Sherry Huang"
output: 
  pdf_document: 
    highlight: pygments
    dev: cairo_pdf
fontsize: 11pt
geometry: margin=1in
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidymodels)
```

```{r}
covid = read_csv("covid_data.csv")
covid
```

# Part 1

# Part 2

# Part 3

Using a different `signal` from the `covid` data (or more!), and/or restricting to any states of your choosing, make any of the time-related plots above, or something related to them. It may be helpful to return to the description of Delphi’s [signal variables](https://cmu-delphi.github.io/delphi-epidata/api/covidcast-signals/fb-survey.html#behavior-indicators) when choosing a signal and creating your titles, axes labels, and legend.

You should make sure to incorporate the following custom elements in your graph:

  + X-axis labels using `scale_x_time` if making a time series
  + Color palette
  + Theme
  + Informative title/subtitle/axes labels/legends, etc. (If you find you do not need one or more of these elements to fully explain what is going on in your graph, you can leave them out if you prefer!)
  
```{r}
ny_events = covid %>%
  filter(signal == "smoothed_large_event_1d" & geo_value == "ny")
ny_events
```
  
```{r}
library(ggthemes)
ggplot(ny_events, aes(x = time_value, y = value, ymin = value - 2*stderr, ymax = value + 2*stderr)) +
  geom_line(col = "red") +
  geom_ribbon(alpha = .1, fill = "red") +
  scale_x_date(date_labels = "%b %Y") +
  labs(
    x = "",
    y = "",
    title = "% of New Yorkers who attended an event \nw/ 10+ people in the past 24 hours",
    subtitle = "Smoothed Estimate",
    caption = "Source: Delphi Symptom Survey"
  ) +
  theme_fivethirtyeight() +
  theme(text = element_text(family = "Tahoma"), plot.title.position = "plot")
```
  