---
title: "Lab11 Write-Up"
author: "Sherry Huang"
output: 
  html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
library(tidyverse)
library(gganimate)
library(ggthemes)
```


# Part 1

[You do not have to include any graphs here, but you can for your own notes if you wish!]

# Part 2

[You do not have to include any graphs here, but you can for your own notes if you wish!]

# Part 3: Your turn! 

Using any data besides `gapminder`, create any animation you want (besides the ones I've included here). Your animations can be similar to Examples 1 and 2, but should include changes beyond plugging in different variables to the `aes` calls.

Everybody should submit an .rmd file with your animation. You should also turn in an HTML document (via RPubs) or use `anim_save()` to save your animation and turn it in alongside your .rmd file: 

`anim_save(FILENAME, animation = last_animation())`

(for more info, use `?anim_save`)

```{r}
life_expectancy =
  read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-07-03/week14_global_life_expectancy.csv")
```

```{r}
worldtilegrid <- read.csv("worldtilegrid.csv")
world_expectancy = left_join(worldtilegrid, life_expectancy, by = c("alpha.3" = "code"))
world_expectancy <- world_expectancy %>% filter(!is.na(year)) %>%
  mutate(year = as.integer(year))


anim_2 <- ggplot(world_expectancy, mapping = aes(x = year, y = life_expectancy, colour = name)
  ) +
  geom_line(show.legend = FALSE, alpha = 0.7) +
  scale_color_viridis_d(option = "C") +
  labs(title = "Life Expectancy over the Years", x = "", y = "life expectancy") +
  facet_wrap(~ region) +
  theme_bw() +
  transition_reveal(year)

animate(anim_2, nframes = 100)
```

